---
title: "eds212_day3_comp2"
---

## Vectors in R!

```{r}
marmots <- c("blue", "green", 4, "yellow", TRUE)

marmots
```

every element of your vector in R has to be the same class to be that class, otherwise, considered character

```{r}
class(marmots)
```

if all values are numeric, they'll be considered that class (numeric)

```{r}
pika <- c(12.4, 6.8, 2.9, 5, 8.8, 20)
pika
class(pika)
```

"Notice in the vector above, these are class *numeric*. If values should be integers (often the case with count data), you can add an `L` after the value." side note -- checking the class is typically only done in the console :)

```{r}
bear <- c(20L, 3L, 5L, 18L, 23L)

class(bear)

bear
```

you might want integers to help w scales on axes ?

here are some changes:)

## Vector addition and subtraction

```{r}
ringtail <- c(4.3, 8.9, 2.6, 7.1)
fox <- c(9.0, 12.5, 5.4, 10.9)

#addition

ringtail + fox

#stored addition:
 ring_plus_fox <- ringtail + fox
```

```{r}
#subtraction

ringtail - fox

rintail_minus_fox <- ringtail - fox
```

```{r}
# scalar multiplier 

100 * ringtail
```

```{r}

# Dot product

ringtail %*% fox
```

run all = ctrl + alt + R

## Matrices in R (for tomorrow...)

```{r}
# oh boy 
```
